\documentclass[a4,12pt]{article}

%--- Packages génériques ---%

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[babel=true]{csquotes}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{textcomp}
\usepackage{float}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{empheq}
\usepackage{color}
\usepackage{cancel}

%--- Structure de la page ---%

\usepackage{fancyheadings}

\topmargin -1.5 cm
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 17 cm
\setlength{\headwidth}{\textwidth}
\textheight 24 cm
\pagestyle{fancy}
\lhead[\fancyplain{}{\thepage}]{\fancyplain{}{\sl MSIAM 3A}}
\chead[\fancyplain{}{{\sl }}]{\fancyplain{}{{Summary of the last meeting}}}
\rhead[\fancyplain{}{}]{\fancyplain{}{Rakotonarivo \& Mazouth--Laurol}}
\lfoot{\fancyplain{}{}}
\cfoot{\fancyplain{}{}}
\cfoot{\thepage }
\rfoot{\fancyplain{}{}}

%--- Raccourcis commande ---%

\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\A}{\mathbf{A}}
\newcommand{\B}{\mathbf{B}}
\newcommand{\C}{\mathbf{C}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\ub}{\mathbf{u}}

\DeclareMathOperator{\e}{e}
%--- Header to write code ---%
\usepackage { listings }
%%configuration de listings
\lstset{
	language=c++,
	basicstyle=\ttfamily\small, %
	identifierstyle=\color{black}, %
	keywordstyle=\color{blue}, %
	stringstyle=\color{black!60}, %
	commentstyle=\it\color{green!95!yellow!1}, %
	columns=flexible, %
	tabsize=2, %
	extendedchars=true, %
	showspaces=false, %
	showstringspaces=false, %
	numbers=left, %
	numberstyle=\tiny, %
	breaklines=true, %
	breakautoindent=true, %
	captionpos=b
}


\usepackage{xcolor}


\definecolor{Zgris}{rgb}{0.87,0.85,0.85}


\newsavebox{\BBbox}
\newenvironment{DDbox}[1]{
	\begin{lrbox}{\BBbox}\begin{minipage}{\linewidth}}
		{\end{minipage}\end{lrbox}\noindent\colorbox{Zgris}{\usebox{\BBbox}} \\
	[.5cm]}
%--- Mode correction et incréments automatiques ---%

\usepackage{framed}
\usepackage{ifthen}
\usepackage{comment}

\newcounter{Nbquestion}

\newcommand*\question{%
\stepcounter{Nbquestion}%
\textbf{Question \theNbquestion. }}

\newboolean{enseignant}
%\setboolean{enseignant}{true}
\setboolean{enseignant}{false}

\ifthenelse{
\boolean{enseignant}}{
\newenvironment{correction}{\begin{shaded}}{\end{shaded}}
}
{
\excludecomment{correction}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 							               EN-TETE        

\title{\textbf{Tomography reconstruction from 2D projections}}
\author{
\begin{tabular}{cc}
	\textsc{Rakotonarivo Michi} & \textsc{Maxime Mazouth--Laurol}
\end{tabular}}   
\date{\small $6^{th}$ December 2017}

\makeatletter
	\def\thetitle{\@title}
	\def\theauthor{\@author}
	\def\thedate{\@date}
\makeatother 

\usepackage{etoolbox}
\usepackage{titling}
\setlength{\droptitle}{-7em}

\setlength{\parindent}{0cm}

\makeatletter
% patch pour le bug concernant les parenthèses fermantes d'après http://tex.stackexchange.com/q/69472
\patchcmd{\lsthk@SelectCharTable}{%
  \lst@ifbreaklines\lst@Def{`)}{\lst@breakProcessOther)}\fi}{}{}{}
\begin{document}

\maketitle

\section{Summary of the last meeting}
\begin{itemize}
\item Agreement on weekly meetings via video chatting or face-to-face if necessary.
\item Discussion about what has already be done. We have been warned that, during this project, only disks would be dealt with, which simplifies significantly the calculation of the line length of intersection of an arbitrary line in 2D with an arbitrary disk : instead of discretizing the projection lines, an analytical length can be computed.
\item As formulae for translation and scaling of the Radon Transform exist, the sinogram of any disk can be derived from the Radon Transform of the unit sphere.
\end{itemize}

\section{Actions to achieve}
\begin{itemize}
\item Modify the code to take above remarks into account.
\item Test out the derived sinograms for scaled and translated disks.
\item Display moments of the projections and compare them with their projections in the trigonometric polynomial basis.
\item Make some disks move during the parallel projection collection(the time variable being our projection angle).
\end{itemize}




\end{document}